---
title: "What is your blogpost title? Add it here??"
subtitle: "Assignment 4 ETC5512"
author: "Trisha Aurielle Andrea"
format: html
editor: visual
---

::: panel-tabset
<!-- Task 1 Tab: Data and Documenting -->

## Data and Documenting

```{r, echo=FALSE}
library(readr)
library(tidyverse)
library(caret)
library(pROC)
library(corrplot)
library(dplyr)
library(ggplot2)
library(e1071)
library(ROSE)
```

#### Topic 

#### Description

#### Dataset link

#### Download Process

#### Data Usage

```{r, warning=FALSE}
heart_data1 <- read.csv("data/heart_2020_cleaned.csv")
heart_data2 <- read.csv("data/heart_disease_health_indicators_BRFSS2015.csv")
head(heart_data1)
head(heart_data2)
```
```{r}
str(heart_data1)
summary(heart_data1)
```

```{r}
str(heart_data2)
summary(heart_data2)
```
```{r}
# Rename columns for consistency
heart_data2 <- heart_data2 %>% rename(
  Smoking = Smoker,
  Diabetic = Diabetes,
  PhysicalActivity = PhysActivity,
  PhysicalHealth = PhysHlth,
  MentalHealth = MentHlth,
  AlcoholDrinking = HvyAlcoholConsump,
  HeartDisease = HeartDiseaseorAttack
)

heart_data2 <- heart_data2 %>%
  mutate(
    Diabetic = ifelse(Diabetic == 2, 1, Diabetic)
  )
```

```{r}
# Convert categorical columns to numerical
heart_data1 <- heart_data1 %>%
  mutate(
    HeartDisease = ifelse(HeartDisease == "Yes", 1, 0),
    Smoking = ifelse(Smoking == "Yes", 1, 0),
    AlcoholDrinking = ifelse(AlcoholDrinking == "Yes", 1, 0),
    Stroke = ifelse(Stroke == "Yes", 1, 0),
    PhysicalActivity = ifelse(PhysicalActivity == "Yes", 1, 0),
    Diabetic = ifelse(Diabetic == "Yes", 1, ifelse(Diabetic == "No", 0, NA)),
    Sex = ifelse(Sex == "Male", 1, 0)
  )

```

```{r}
# Select common columns
common_columns <- c("HeartDisease", "BMI", "Smoking", "AlcoholDrinking", "Stroke",
                    "PhysicalHealth", "MentalHealth", "Sex", "Diabetic", "PhysicalActivity")

heart_data1 <- heart_data1 %>% select(all_of(common_columns))
heart_data2 <- heart_data2 %>% select(all_of(common_columns))
```

```{r}
# Combine datasets
combined_data <- bind_rows(heart_data1, heart_data2)
```


```{r, warning=FALSE}
# Perform exploratory data analysis (EDA)
correlation_matrix <- cor(combined_data, use = "complete.obs")
corrplot(correlation_matrix, method = "ellipse", type = "upper",
         tl.col = "black", tl.cex = 0.8,
         addCoef.col = "black", number.cex = 0.7,
         order = "hclust", addrect = 2)

print(table(combined_data$HeartDisease))
ggplot(combined_data, aes(x = as.factor(HeartDisease))) +
  geom_bar(fill = "steelblue") +
  labs(title = "HeartDisease Distribution", x = "Heart Disease (0 = No, 1 = Yes)", y = "Count")

# Boxplots for BMI, PhysicalHealth, and MentalHealth
numerical_features <- c("BMI", "PhysicalHealth", "MentalHealth")

for (feature in numerical_features) {
  print(
    ggplot(combined_data, aes_string(y = feature)) +
      geom_boxplot(fill = "steelblue", color = "black", outlier.color = "red", outlier.shape = 16) +
      labs(title = paste("Boxplot of", feature), y = feature) +
      theme_minimal()
  )
}
```
```{r}
# Convert target variable to a factor
combined_data <- combined_data %>%
  mutate(
    HeartDisease = as.factor(HeartDisease),  
    Smoking = as.factor(Smoking),
    AlcoholDrinking = as.factor(AlcoholDrinking),
    Stroke = as.factor(Stroke),
    PhysicalActivity = as.factor(PhysicalActivity),
    Sex = as.factor(Sex),
    Diabetic = as.factor(Diabetic),
    BMI = as.numeric(BMI),
    PhysicalHealth = as.numeric(PhysicalHealth),
    MentalHealth = as.numeric(MentalHealth)
  )

str(combined_data)
```

```{r}
# Train-test split
set.seed(123)
train_index <- createDataPartition(combined_data$HeartDisease, p = 0.7, list = FALSE)
train_data <- combined_data[train_index, ]
test_data <- combined_data[-train_index, ]

str(train_data)
table(train_data$Diabetic)
set.seed(123)
```


<!-- Task 2 Tab: Writing your blogpost -->

## Blog post

### What's in this section

Here is where you should write your blogpost! (Task 2)

### Blogpost Structure

There is no strict structure for you to follow. However, here is a skeleton structure you may find helpful.

1.  Title (is set at the top of this document)
2.  Motivation\
3.  Data\
4.  Analysis\
5.  Conclusions\
6.  References



<!-- Task 3 Tab: Behind the Scenes -  -->

## Behind the Scenes

### What's in this section

Here is where you should tell us about your reflection on your analysis (Task 3).

Again, these are the details about **your** perspective and the gritty details behind the scenes of your analysis.
:::
